Cognate Priming: Report

### 2021-10-21 Rmd/report.Rmd
Fix renv

---
title: "Cognate Priming: Report"
output:
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dpi = 150,
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		knitr.duplicate.label = "allow",
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

>>>>

---
title: "Cognate Priming: Report"
output:
  github_document:
    pandoc_args: --webtex
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dpi = 150,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
		knitr.duplicate.label = "allow",
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)
